%Chapter 4
\chapter{Research Findings}
\label{Chapter4}
\section{Run results and Analysis tools}
In order to test the null hypothesis, 30 such samples of the kind described
in chapter 3 were collected. The content of the samples appear in the following
tables.




These results are clearly not what we expect if the null hypothesis is true.
Testing of this hypothesis can be done with the machinary of classical
statistics, specifically by calculating the exact probability of the results
by working out the exact sampling distribution and by obtaining how likely these
results are to come from the various appropriate distributions where
the performances are equal by running the results thru the machinary of the
t-test. A description of each of these statistical methods follows.

\subsection{Exact Sampling Distribution}
The following description losely follows the procedure described in \cite{Cohen}.
In it, the author asks you to imagine testing a coin to see whether or not it
is fair, flipping the coin 1,2,..N times. He then asks you to consider whether
some proportion of heads is actually fair from 0/N, 1/N.., N/N heads. The
propability that some proportion of heads p = i/N is fair can be calculated
exactly with the binomial distribution $$\frac{N!}{i!(N-i)!}r^{i}(1-r)^{N-i}$$.
This situation is analogous to the number of first, second, or third place
finishes some meta-algorithm obtained in this thesis experiment. The probabilty
of proportion for each of the meta-learning algorithms can be seen in table

\begin{table}
\begin{tabular}{|r|r|r|r|}
\hline
    &   GuessesActive &   GuessesEx &   GuessesSamp \\
\hline
  0 &        -7.2863  &    9.15791  &      -2.78077 \\
\hline
  1 &         2.26812 &   -0.137718 &      -2.06779 \\
\hline
  2 &         4.99363 &  -13.1737   &       4.13425 \\
\hline
\end{tabular}
\caption{Averaged t scores}
\end{table}

T test equation where s is the sample standard deviation and N is the number of
samples, overscore x is an individual samples mean/calculated value, mu is the
population mean/expected value

$$t =\frac{\overline{x}-\mu}{\hat{\sigma}_{\overline{x}}} = \frac{\overline{x}-\mu}{\frac{s}{\sqrt{N}}}$$
