%Chapter 5
\chapter{Conclusion and Future Work}
\label{Chapter5}
In this thesis, I proposed that the no free lunch hypotheis might not apply to
meta learning algorithms. In order to test this hypothesis, I first built a
system to determine the accuracy of three meta learning strategies:
Exhaustive, Active, and Sampling. To use these strategies, a base of
datasets would first be randomly choosen from the collection of all available
datasets that had been gathered from the UCI Irvine data repository.
Each strategy would then be carried out on the metabase and make an
estimate as to what algorithm would result in the highest classification
accuracy. Each algorithm would make this guess for each dataset in the
collection of available datasets excluding the datasets within the current
metabase. A new metabase would then be choosen at random and the process would be
repeated 9 more times, giving a number between 0 and 10 for how many times
each algorithm got the First, second, or third most correct guesses.
This process was repeated 30 times, resulting in 30 samples. $t$ test analysis
was then performed, giving an an average among the absolute values of each of
the position $t$ scores of 5.11, allowing us to reject the null
hypothesis at a 5 percent margin of error.

Future work could involve repeat runs of the system described in this thesis
with more datasets, which would test the results in a wider variety of problem
domains, therefore strengthening the results. Other interesting variations of
this experiment could come from testing the results with diffrent meta features,
testing the results with noisy datasets, and even testing the results with
artificially generated datasets. One could also test the results of this
procedure with an intermediary parameter tuning step, that is to say
we could tune the parameters of the various base algorithms to fit the domain
of the dataset currently being analyzed. Also, a future researcher might also
choose to vary the algorithm used to classify the meta features, as here we
make use of the k-means clustring algorithm to make our choice from the meta
features of our modified meta bases and the selection of a different algorithm
could change the results.
